Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-02-02 paper.tex
Methodology review

There are several issues inherent to the problem of predicting sales of new 
products: the limitation on the amount of data available, the application of 
different methods and choose the most suitable of them.
In addition, there is no a standard methodology to solve the general problem 
of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
Usually, a preliminary analysis of the data is carried out to eliminate those 
variables that describe the product but do not provide useful information during 
the prediction process.

\hspace{2cm}
\begin{verbatim}
  Stage 1: Collecting and analyze data
		- Variables selection
 		- Data preprocesing
  Stage 2: Select the best forecasting method
 		- Obtaining and evaluating forecasting models
 		- Calculate forecasting values
  Stage 3: Subjectively adjust obtained results
	 	- Apply additional expert knowledge, such as information 
 	 	  about seasonality, trends, etc.
\end{verbatim}

% Maribel: quito la figura por el issue asignado por antonio mora.
%\begin{figure}[!ht] 
%\begin{center}
%  \epsfig{file=stages.eps,width=7cm}
%\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
%methods testing, and (3) subjectively adjusting the obtained results.}}
%\label{fig:stages}
%\end{center}
%\end{figure}

Thus, in this study two main stages are proposed: 
\begin{itemize}

  \item  First, after the editorial company has provided the raw data, taken 
  directly from its database, a feature selection is carried out, as it is 
  an effective dimensionality reduction technique and an essential preprocessing 
  method to remove noise features \cite{Krishnapuram2004}. The idea of these 
  algorithms is searching the space of attribute subsets to find out which one 
  in the data works best for classification or prediction.
  In this stage, the information obtained using several feature selection 
  methods as well as analyzing the SOM cluster method results is used to 
  remove some unrelated variables and selects the best variables to be 
  considered in the forecasted model. % we will use pre-sales data.
  This task may help to identify leading indicators to be used by the 
  forecasting methods in order to improve the accuracy of future forecasts.

  \item  Then, several forecasting methods have to be tested. In this stage 
  different forecasting methods are used to obtain sales forecasts from the 
  data provided.

%In some cases, depending on the company needs and after obtaining the forecasting  results, it is necessary a third stage where experienced managers adjust subject1ively the results obtained using the forecasting methods (see Figure \ref{fig:stages} for details). Esta frase no aporta nada que no esté dicho ya antes en los comentarios de las tres etapas que antes estaban en una figura, así que quito la frase entera: Maribel

They might manually adjust the forecasting results taking into account their 
knowledge in industry experience and their perception about trends.

@@

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations \cite{gepsoft} in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka \cite{pentaho,Witten2011} 
or R \cite{otexts,Hyndman2013}, are
proposed.
Specifically, in order to compute the forecasting errors of the different methods, 
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

@@

In general, historical data is used to make time series, and from them extracting 
common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns 
are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010} (only pre-sales data is available in this problem).
% (Paloma) - Se deberían evitar paréntetis.

@@

Feature extraction is a ``transformation-based approach", therefore it transforms the original meaning of the features. This approach involves creating a subset of new features by combinations of the existing features, thus is employed when the semantics of the original dataset will not be needed by any future process. On the contrary, feature selection attempts to retain the meaning of the original feature set. It is part of what is called semantic-preserving techniques, known as ``selection-based approaches". By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}. In the problem this work assesses, it is very important to maintain the semantics of the set of initial variables, and therefore several feature selection methods have been applied.

>>>>

There is no a standard methodology to solve the general problem of sales forecasting. %FERGU: hacer más hincapié de esto en la intro entonces
In this work we have followed these steps:

\hspace{2cm}
\begin{verbatim}
  Step 1: Collect and analyse data
       - Data preprocessing
       - Feature selection
  Step 2: Select the best forecasting method
       - Evaluate forecasting models
       - Perform forecast
  Step 3: Subjectively adjust obtained results
      - Apply additional expert knowledge, such as information 
        about seasonality or trends.
\end{verbatim}

%Usually, a preliminary analysis of the data is carried out to eliminate those 
%variables that describe the product but do not provide useful information during 
%the prediction process.

The steps are described i the following paragraphs.

First, after the editorial company has provided the raw data, extracted directly from its database, a preprocessing method is performed in order to remove incorrect or incoherent patterns, such as those with null values in required variables, or with negative sales, for instance. Moreover, the initial set of variables is reduced by an expert to use just those that can be known in advance when a new book is launched, i.e. \textit{pre-sales data}.

Then, a Feature Selection process \cite{kittler1986feature} is carried out, as it is an effective dimensionality reduction technique and an essential preprocessing method to remove `noisy' (non-useful) features \cite{Krishnapuram2004}. The aim of these algorithms is exploring the space of attributes to find out which subset of them yield the best results in a classification or prediction problem.
  In this stage, both, numerical and visualisation-based approaches has been applied, in order to select the best variables for the forecasting methods.
  This task may also help to identify leading indicators to be considered by a human expert ti do predictions.

After this process, several forecasting methods have been tested, considering different approaches, such as rule- or tree-based, together with numerical methods. 
% Antonio - is 'numerical' the best term for these kind of methods?
The obtained results are then compared.

@@

In the literature different error measures can be found to evaluate the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
We have used the widely accepted standard equations \cite{gepsoft} in order to compare the obtained results with those presented in other research papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), implemented in tools like Weka \cite{pentaho,Witten2011} 
or R \cite{otexts,Hyndman2013}, are considered.
Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:

@@

The created forecasting models and results, along with the selected subset of features, are analysed and presented to the experts in order to aid his/her decision. They might manually adjust the forecasting results taking into account their knowledge in industry experience and their perception about trends.

@@

In general, historical data is used to make time series, and from them extracting 
common patterns and obtaining accurate predictions.
However, in the case of new products, such as the issue of new books, past patterns are difficult to observe as there is no available historical sales data 
\cite{ChingChin2010} (only pre-sales data are available in this problem).
% (Paloma) - Se deberían evitar paréntetis.

@@

Feature extraction is a ``transformation-based approach'', therefore it transforms the original meaning of the features. This approach involves creating a subset of new features by combinations of the existing features, thus is employed when the semantics of the original dataset will not be needed by any future process. On the contrary, feature selection attempts to retain the meaning of the original feature set. It is part of what is called semantic-preserving techniques, known as ``selection-based approaches". By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}. In the problem this work assesses, it is very important to maintain the semantics of the set of initial variables, and therefore several feature selection methods have been applied.
